---
title: "Building a Model for weight and systolic bp of male people aging 25-30"
author: "Nithya S"
date: "2023-11-03"
output: word_document
---
# Objective

•	Obtaining the scatter plot and interpreting.
•	Finding the regression line connecting the variables systolic bp and weight. To interpret the plot, intercept term and the regression coefficients. To infer from the sign of regression coefficient.
•	Obtaining the fitted values. To check if the sum of fitted values is equal to the sum of observed values.

URL for the dataset: 

***https://docs.google.com/spreadsheets/d/1WXzKqlu21X3qhfAWn1-FaoY3OkLI78VD/edit?usp=sharing&ouid=110138716074493614410&rtpof=true&sd=true***


# Procedure and analysis

We import the dataset from excel in order to proceed further.
We import the dataset as follows

```{r }
library(readxl)
Dataset <- read_excel("G:/My Drive/Linear Regression/Datasets/Dataset.xlsx")
View(Dataset)
attach(Dataset)
```
Now that we have attached the dataset, we now proceed to build the model.

## To check the relationship between the variables under study

### 1. By plotting 

```{r }
plot(Dataset$Weight,Dataset$`Symbolic BP`,col="purple",main="Weight and Systolic BP Regression ",xlab="weight in pounds",ylab="Systolic bp in mmhg")
```

### 2.By Karl Pearson's correlation co-efficient

```{r }
cor(Dataset$Weight,Dataset$`Symbolic BP`)
```

#### We give a regression equation

```{r }
model=lm(Dataset$`Symbolic BP`~Dataset$Weight)
model
summary(model)
```
### To plot the observations with a smooth line

```{r }
plot(Dataset$Weight,Dataset$`Symbolic BP`,col="purple",main="Weight and Sysbolic BP Regression ",xlab="weight in pounds",ylab="Sysbolic bp in mmhg")

scatter.smooth(Dataset$`Symbolic BP`,Dataset$Weight,col="purple",main="Weight and Sysbolic BP Regression ",xlab="weight in pounds",ylab="Sysbolic bp in mmhg")
```

#### Fitted lines in a scatter diagram

```{r }
plot(Dataset$Weight,Dataset$`Symbolic BP`,col="purple",main="Weight and Sysbolic BP Regression ",xlab="weight in pounds",ylab="Sysbolic bp in mmhg")

scatter.smooth(Dataset$`Symbolic BP`,Dataset$Weight,col="purple",main="Weight and Sysbolic BP Regression ",xlab="weight in pounds",ylab="Sysbolic bp in mmhg")

abline(lm(Dataset$Weight~Dataset$`Symbolic BP`))
```

### To obtain the fitted values

```{r }
Fit=fitted.values(model)
Fit
```

To see if the sum of the fitted values is equal to the sum of the observed values.
First we sum the fitted values. Then we sum the Systolic bp values and check if they both are the same as follows.

```{r }
sum_fit=sum(Fit)
sum_fit

sum_sysbp=sum(Dataset$`Symbolic BP`)
sum_sysbp
```