---
title: "Non linear regression model"
author: "Nithya S"
date: "2024-01-12"
output: word_document
---
# Objective

To represent the substrate concentration (S) and the observed velocity (v) based on an enzymology experiment.

(a) Fit a non linear regression model that relates velocity to concentration using Michaelis-Menten equation .
(b) Analyse and examine whether you can fit a simple linear regression model that relates velocity and substrate concentration by using any suitable transformation.

URL for the dataset:

***https://docs.google.com/spreadsheets/d/1X_rJrknx0vAdunPST5Dh0PQKffC5LeDE/edit?usp=sharing&ouid=110138716074493614410&rtpof=true&sd=true***

We import the data to perform the analysis as follows:

```{r }
library(readxl)
Dataset <- read_excel("G:/My Drive/Linear Regression/Datasets/Substrate concentration.xlsx")
View(Dataset)
attach(Dataset)
```

To start off, we plot the data as follows:

```{r }
plot(S,V,col="hotpink",main="Relationship between concentration and velocity",xlab="Concentration",ylab="Velocity")
```

We fit the non linear regression model that relates velocity to concentration using Michaelis-Menten equation as follows.

```{r }
MM_model=nls(V~V_max*S/(K_m+S),start=c(V_max=72,K_m=5),data=Dataset)
summary(MM_model)
plot(S,V,col="hotpink",main="Relationship between concentration and velocity",xlab="Concentration",ylab="Velocity")
lines(S,predict(MM_model,lty=1,col="blue",lwd=3))
```

We also see from the summary that, the regression coefficients are significant at 5% significance level. 
Since the values are significant, we proceed for residual analysis. 

```{r }
residual=resid(MM_model)
residual
plot(residual)
abline(0,0)
```

Now to check for Normality condition

```{r }
qqnorm(resid(MM_model)) # QQ plot-of residual
qqline(resid(MM_model)) # plots the points
```

Hypothesis to testing for normality:
H0: Errors follows normal distribution.
v/s
H1: Errors do not follow normal distribution.

Normality using shapiro test

```{r }
shapiro.test(resid(MM_model))

```

The above model will reduce to a linear model when simplified.

```{r }
library(readxl)
New_data <- read_excel("G:/My Drive/Linear Regression/Datasets/Substrate concentration.xlsx")
View(New_data)
attach(New_data)

```

We plot the above in a graph to understand the relationship now that we have taken the inverse

```{r }
S_new=1/S
V_new=1/V

plot(S_new,V_new,col="hotpink",main="Relationship between concentration and velocity",xlab="Concentration",ylab="Velocity")
```

The non-linear model has now become a linear model due to inverse transformation which is visible in the graph.
Now we build a linear regression model for the transformed variables and validate the same.

```{r }
Reg_model=lm(V_new~S_new)
Reg_model
summary(Reg_model)
```

We also see from the summary that, the regression coefficients are significant at 5% significance level. 
Since the values are significant, we proceed for residual analysis. 

We check for the normality by
1. QQ-plot
2. Shapiro test

```{r }
qqnorm(resid(Reg_model)) # QQ plot-of residual
qqline(resid(Reg_model)) # plots the points
```

Hypothesis to testing for normality:
H0: Errors follows normal distribution.
v/s
H1: Errors do not follow normal distribution.

```{r }
shapiro.test(resid(Reg_model))
```

Hypothesis testing for constant variance :
To test if the errors have constant variance.
H0: errors have constant variance
v/s
H1: errors have no constant variance

```{r }
library(lmtest)
bptest(Reg_model)

```