---
title: "Polynomial regression model for inbuilt dataset 'pressure'"
author: "Nithya S"
date: "2024-01-08"
output: word_document
---
# Objective:

1. By using the inbuilt data set "pressure" in R, fit a suitable linear regression model that relates pressure and temperature.
2. Also, perform residual analysis and comment about the possibility of modelling non linear regression model for the data set.

First we call for the data and plot the same.

```{r }
data=pressure
data
```

```{r }
plot(data$temperature,data$pressure,main="Realtionship of temperature and pressure",col='hotpink',xlab="temperature",ylab="pressure")
```

To fit a polynomial regression model, we proceed as follows:

```{r }
model=lm(pressure~temperature+I(temperature^2),data=data)
model
summary(model)
plot(data$temperature,data$pressure,main="Realtionship of temperature and pressure",col='hotpink',xlab="temperature",ylab="pressure")
lines(smooth.spline(data$temperature,predict(model)),col="hotpink",lwd=3)
```

i) First, we get the residuals of the model and plot the obtained residuals with fitted values in order to understand the linearity, constant variance and outliers of the model.

```{r }
fitted_values=fitted.values(model)
fitted_values

plot(fitted_values,resid(model),col="hotpink",main="Fitted values and Residual values",xlab="fitted values",ylab="residual values")
abline(0,0)
```

Let us use standardized residuals. The procedure is as follows:

```{r }
plot(fitted_values,rstandard(model),col="hotpink",main="Fitted values and Standardized values",xlab="fitted values",ylab="standardized values")
abline(0,0)
```

To be very precise we can even check in the residual values for outliers as follows:

```{r }
residual=rstandard(model)
residual
plot(residual)
```

Since, there are no outliers in the model, we proceed further.

ii) Now, we check if the normality assumption is satisfied by using 
1. QQ plot
2. Shapiro test

The QQ plot is as follows:

```{r }
resi=resid(model)

qqnorm(resi) # QQ plot-of residual

qqline(resi) # plots the points
```

The Shapiro test is as follows:

Hypothesis to testing for normality:
H0: Errors follows normal distribution.
v/s
H1: Errors do not follow normal distribution.

```{r }
shapiro.test(residual)
```

Hypothesis testing for constant variance :
To test if the errors have constant variance.
H0: errors have constant variance
v/s
H1: errors have no constant variance

```{r }
library(lmtest)
bptest(model)
```